Xolotl: An Intuitive and Approachable Neuron and Network Simulator for Research and Teaching

### 2018-08-17 paper/paper.tex
added funding info
diff --git a/README.md b/README.md
index 4699fb8..9a34667 100644
--- a/README.md
+++ b/README.md
@@ -1,7 +1,19 @@
-# xolotl: An Intuitive and Approachable Neuron & Network Simulator in MATLAB
+# xolotl: An Intuitive and Approachable Neuron & Network Simulator

 This repository contains code, latex documents and supporting images that allows you to reproduce all figures and text in this paper.

+# Status
+
+This paper is now at the "preprint" stage, and has been submitted. You can read it on the arXiv [here]()
+
+
+# Structure
+
+The Latex source for the paper is in `paper/`

\title[Xolotl: neuron and network simulator]{xolotl: An Intuitive and Approachable Neuron and Network Simulator for Research and Teaching}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{An Intuitive Neuronal Simulator}

@@

	\tiny
	\keyFont{ \section{Keywords:} simulator, code:MATLAB, code:C++, conductance-based, neuron, network, neuron models}

@@

AH received funding from the National Institute on Drug Abuse (NIDA) through the undergraduate training grant in computational neuroscience (R90DA033463-01).

>>>>

\title[Xolotl: neuron and network simulator]{Xolotl: An Intuitive and Approachable Neuron and Network Simulator for Research and Teaching}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{An Intuitive Neuronal Simulator}

@@

	\tiny
	\keyFont{ \section{Keywords:} code:MATLAB, code:C++, conductance-based, software, Hodgkin-Huxley}

@@

The authors acknowledge funding from the National Institute on Drug Abuse (NIDA) through the undergraduate training grant in computational neuroscience R90DA033463 (AH), T32NS007292-31 (SG-S) and R35 NS097343 (EM).
